Pillar 1 - Sequential Pattern Mining

### 2019-01-16 Pillar 1 - Sequential Pattern Mining.Rmd
puts transcript data into transaction format

```{r library, message = F}
library(tidyverse)
library(arules)
library(arulesSequences)
```

@@

SequenceID = `Student ID Number`
Event ID   =  UCM_YEAR_Period OR Year_period. 
Items      =  Course
```{r}
d_sequence_transactions <- d_course %>%
  select(Type, Code, Letters) %>%
  filter(Type == "Elective",
         ! Letters %in% c("SKI", "PRO"),
         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
  select(Code) %>%
  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
  mutate(Time= paste(`Civil Year`,Period, sep="")) %>%
  select(Code,`Student ID Number`, Time) %>%
  group_by(`Student ID Number`, Time) %>%
  arrange(Time,`Student ID Number`) #%>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
  #summarize(list_course = list(Code)) %>%
  #group_by()   #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")

sequence_transcript_data <- data.frame(item=d_sequence_transactions$Code)

transcripts.tran <- as(sequence_transcript_data, "transactions")

 transactionInfo(transcripts.tran)$sequenceID <- d_sequence_transactions$`Student ID Number`

 transactionInfo(transcripts.tran)$eventID <- d_sequence_transactions$Time

inspect(head(transcripts.tran))

```
now we find frequent sequential patterns
```{r}
frequent_trajectories <- cspade(transcripts.tran, parameter = list(support = 0.50))
```

>>>>

```{r library, message = F}
#detach(package:tm, unload=TRUE) #there is overlap with tm package in inspect()

library(tidyverse)
library(arules)
library(arulesSequences)
```

@@

SequenceID = `Student ID Number`
Event ID   =  UCM_YEAR_Period OR Year_period. 
Items      =  Course
```{r}
d_sequence_transactions <- d_course %>%
  select(Type, Code, Letters) %>%
  filter(Type == "Elective",
         ! Letters %in% c("SKI", "PRO"),
         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
  select(Code) %>%
  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
  mutate( Time = paste(Year_numerical, Period, sep = ""),
          Time = as.double(Time)) %>%
  select(`Student ID Number`, Code, Time) %>%
  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
  group_by(`Student ID Number`, Time) %>%
  summarize(list_course = list(Code)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))

list_course <- d_sequence_transactions$list_course
names(list_course) <- d_sequence_transactions$TransactionID

my_transactions <- as(list_course, "transactions")
transactionInfo(my_transactions)$sequenceID <- d_sequence_transactions$`Student ID Number`
transactionInfo(my_transactions)$eventID <- d_sequence_transactions$Time
transactionInfo(my_transactions)$transactionID <- NULL

```

now we find frequent sequential patterns. 
The parameter values are: 
support:  a numeric value specifying the minimum support of a sequence (default 0.1, range [0,1]).

maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
maxlen:   an integer value specifying the maximum number of elements of a sequence (default 10, range > 0).
mingap:   an integer value specifying the minimum time difference between consecutive elements of a sequence (default none, range >= 1).
maxgap:   an integer value specifying the maximum time difference between consecutive elements of a sequence (default none, range >= 0).
maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).
```{r}
frequent_trajectories <- cspade(my_transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
summary(frequent_trajectories)
as(frequent_trajectories, "data.frame")

inspect(head(frequent_trajectories))

```
